PDBF Testdokument

### 2015-02-25 test.tex
- removed some unused stuff from test.tex - adjusted scale of chart images to html size - chart legend position fixed

\documentclass{scrartcl}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsfonts}
\usepackage{amsmath,amssymb,amstext}
\usepackage[automark]{scrpage2}
\usepackage[bottom]{footmisc}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{listings}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{PDBF}
\usepackage{tabularx}
\usepackage{wrapfig}
\usepackage[a4paper,vmargin={30mm,40mm},hmargin={28mm,28mm}]{geometry}
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}
\title{PDBF Testdokument}
\author{
 Patrick Bender\\
  \texttt{s9pabend@stud.uni-saarland.de}
  \and
 Christian Goldstein\\
  \texttt{c.goldstein@goldstein-systemberatung.de}
}
\date{\today{}, Saarbrücken}
\pagestyle{plain}
\clearscrheadfoot
\cfoot[]{\pagemark}
\lstset{
basicstyle=\ttfamily,
commentstyle=\itshape,
keywordstyle=\bfseries,
    frame=single,
    breaklines=true,
    postbreak=,
keepspaces=true
}
\sloppy

\makeatletter
\def\@maketitle{%
  \vspace*{-\topskip}      % remove the initial space
  \begingroup\centering    % instead of \begin{center}
  \let \footnote \thanks
  \hrule height \z@        % to avoid the insertion of lineskip glue
    {\LARGE \@title \par}%
    \vskip 1.5em 
    {\large
      \lineskip .5em 
      \begin{tabular}[t]{c}%
        \@author
      \end{tabular}\par}%
    \vskip 1em 
    {\large \@date}%
  \par\endgroup            % instead of \end{center}
  \vskip 1.5em             % <--- modify this to adjust the separation
}
\makeatother

\definecolor{pblue}{rgb}{0.13,0.13,1}
\definecolor{pgreen}{rgb}{0,0.5,0}
\definecolor{pred}{rgb}{0.9,0,0}
\definecolor{pgrey}{rgb}{0.46,0.45,0.48}
\lstset{language=Java,
  showspaces=false,
  showtabs=false,
  breaklines=true,
  showstringspaces=false,
  breakatwhitespace=true,
  commentstyle=\color{pgreen},
  keywordstyle=\color{pblue},
  stringstyle=\color{pred},
  basicstyle=\ttfamily\scriptsize,
  moredelim=[il][\textcolor{pgrey}]{$$},
  moredelim=[is][\textcolor{pgrey}]{\%\%}{\%\%}
}

>>>>

\documentclass{scrartcl}
\usepackage{PDBF}
\usepackage{wrapfig}
\usepackage[a4paper,vmargin={30mm,40mm},hmargin={28mm,28mm}]{geometry}

\title{PDBF Testdokument}
\author{
 Patrick Bender\\
  \texttt{s9pabend@stud.uni-saarland.de}
  \and
 Christian Goldstein\\
  \texttt{c.goldstein@goldstein-systemberatung.de}
}
\date{\today{}, Saarbrücken}

\makeatletter
\def\@maketitle{%
  \vspace*{-\topskip}%
  \begingroup\centering%
  \let \footnote \thanks
  \hrule height \z@%
    {\LARGE \@title \par}%
    \vskip 1.5em 
    {\large
      \lineskip .5em 
      \begin{tabular}[t]{c}%
        \@author
      \end{tabular}\par}%
    \vskip 1em 
    {\large \@date}%
  \par\endgroup%
  \vskip 1.5em%
}
\makeatother
